### 2020-12-04 doc/manuscript/Dow_manuscript.Rmd
tree rings caption

tree_rings_caption <- "Figure 6. Climate sensitiivity of annual growth from tree-rings. THIS IS JUST A PLACEHOLDER TO SHOW THE RESULTS--WE'LL WANT TO RE-MAKE FIGURE."

>>>>

tree_rings_caption <- "Figure 6. Climate sensitiivity of annual growth, as derived from tree-rings, for dominant ring- and diffuse- porous species at the Smithonian Conservation Biology Institute and Harvard Forest. Shown are Pearson correlations between ring-width index and and monthly Tmax. Species codes are as given in Table 2."
